---
title: "M2T3"
author: "Team Sergi, Andreu, Paul"
date: "17/07/2019"
output:
  #pdf_document: default
  html_document: default
---
# **Executive summary**  

# **Case**  

> The sales team of Blackwell Electronics ask for another analysis regarding sales performance of certain products in one of their stores. This time, the analysis aims again at the prediction of sales performance but taking the product type into account to see whether and how specific product types outperform others. Therefore, the historical sales data on sales volume has to be analysed again to assesses whether the inclusion of 'product type' has positive impact on predictability and finally to predict sales volume of new products. The four product types are:  
PC, Laptops, Netbooks and Smartphones.  
Additionally, Blackwell expresses their interest in assessing the impact of service reviews and customer reviews on sales performance.  

**Procedure**  
  
> The analysis followed the common data mining approach containing data the steps exploration, pre-processing, modelling and optimization, prediction, and evaluation.  
For the analysis the statistical programming language R with different packages (e.g. 'caret' was used to apply several prediction techniques).  
In particular, correlation Matrix, Random Forest and ANOVA test are applied to assess the importance of 'product type' and other attributes.  

**Results**

> The predicted sales volume is ordered from highest to lowest sales volume in Table 1.  
  
> Table 1: Pred. Volume and profit by brand  
  
Product Type | Brand    | Pred. Volume  | Profit (in k$)
------------ | -------  | ------------- | --------------  
Netbook	     |Acer	    | 734           | 22 
PC	         |Dell1	    | 267           | 47 
Smartphone	 |Samsung2  | 267           | 2 
Laptop	     |Apple	    | 225           | 27
Smartphone	 |Motorola1	| 181           | 4
Smartphone	 |Motorola2	| 167           | 6
PC	         |Dell2	    | 152           | 26
Netbook	     |Asus	    | 137           | 7
Smartphone	 |HTC	      | 134           | 3
Netbook	     |hp	      | 101           | 3
Netbook	     |Samsung1	| 95            | 3
Laptop	     |Toshiba	  | 77            | 14
Laptop	     |Razer	    | 0             | 0  
  
> Table 2 - Total volume and profit by product categories  
  
Category    | Total Sales | Profit (in k$)
------------| ----------- | --------------
Netbooks	  | 1067        | 35
Smartphones	| 749         | 15
PC          | 419         | 73
Laptop      | 302         | 41  
  
> The results show that, in terms of sales, the most sold product type would be Netbooks. In this category, our model has predicted the highest sales volume by far to be the Acer Netbook. Following in categories, Smartphones come in second, with Samsung being the most popular. Next are PCs, and last are laptops, coming close. However, the last two (PCs and Laptops) have the highest profit.  
Addressing the interest in incorporating Product Type into our analysis, it unveiled that there is no impact on using the mentioned Product Type when we are trying to predict sales.  
As far as the impact is on service and customer reviews, we concluded the following: The Positive Reviews, followed by the 4 and 3 stars had the highest impact on our prediction models.  
Additionally, the predicted results agree with the previous analysis using RapidMiner.


**Limitations**  

> The dataset has limited products (80). A much larger number would increase the accuracy of the prediction.
Some of the parameters of each product are barely relevant for our analysis. For instance, the dimensions (width, height and depth) cannot predict sales in our case.  
Similarly, the Best Sellers Rank is missing many values and had to be excluded for analysis.


**Recommendations**  

> Consider the results to be only estimates and should only contribute to decision-making indicatively.  
For further analysis, an expanded dataset in terms of products and a starting to record sales from now on with the purpose of contributing to a more meaningful analysis.  


# **Technical documentation**
# Table of contents
1. [Data Exploration and preprocessing](#Data Exploration and preprocessing)
    1. [Dealing with repeated products](#Dealing with repeated products)
    2. [Removing useless columns](#Removing useless columns)
    3. [Checking for outliers](#Checking for outliers)
2. [Feature Engineering](#Feature Engineering)
3. [Modelling](#Modelling)
4. [Analyzing and Plotting Errors](#Analyzing and Plotting Errors)
5. [Final Predictions](#Final Predictions)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Setup, include=FALSE}
# Load libraries
#install.packages("pacman")
library(pacman)
p_load(caret, lattice, readr, Metrics, corrplot, e1071, mlr, recipes, ggplot2, C50, party, reshape, dplyr,markdown, ggpubr, tidyr, hydroGOF, BBmisc, tidyverse, textclean, inum, doParallel, Hmisc, caretEnsemble, mboost, cluster, ade4, factoextra, asbio, SatMatch, FactoMineR, fpc,e1071, randomForest, rstudioapi, MASS, ParamHelpers, mlr)

# Enable parallel computing
cl <- makePSOCKcluster(4)
registerDoParallel(cl)

#disable scientific notation
options(scipen = 999)

# Loading dataset(s)
#current_path = getActiveDocumentContext()$path
#setwd("C:/Users/Paul/Desktop/Ubiqum/Module 2/2.3 Multiple Regression/Git/Profitability")

ExistProd   <- read.csv("existingproductattributes2017.csv")
NewProd     <- read.csv("newproductattributes2017.csv")
NewProd_Raw <- read.csv("newproductattributes2017.csv")
```
<a name="Data Exploration and preprocessing"></a>  
  
## 1.DATA EXPLORATION AND PREPROCESSING
## 1.1.Dealing with repeated products
```{r}
#Because we have worked with these products before, and because the dataset is small, we can observe duplicates just by looking at the df itself. We find out all 'ExtendedWarranty' products share the same values in everything (including exact number of reviews of all types) except for a small different in price. In a business sense, We conclude this is because warranties are sold alongside different products, only the same type of warranty is included, but will vary in price proportionally to the price itself. We should treat them as the same products and remove all but one.

#Showing the 6 duplicates:
#IMPORTANT NOTE: It's good practice to remove the columns by name instead of by column number, so that if we do changes in dataset later, and we reload these commands, we won't mess up unwanted columns.

sum(duplicated(ExistProd[,c(1,4:18)]))
#Removing them, but setting an average price for the remaining product of Warranty:
#ExistProd <- ExistProd[-c(35:41),]
Duplicates <- ExistProd[c(32:41),]
Duplicates[3,3] <- sum(Duplicates[3:10,3])/8
Duplicates <- Duplicates[1:3,]
ExistProd  <- ExistProd[-c(32:41),]
ExistProd  <- rbind(ExistProd, Duplicates)
```
## 1.2.Removing useless columns
```{r}
#We checked in the previous project that some columns were not useful and just added noise to our prediction model. The columns are:
#1. Product dimensions (width, Depth and Height)
#2. Best Sellers Rank
#3. Shipping Weight
#4. Product Num (we don't want the id to add 'noise')

#We proceed to get rid of the aforementioned columns in both df (they don't need to be the same for prediction, but it's good practice)

ExistProd <- dplyr::select(ExistProd,-c(ProductNum,BestSellersRank,ShippingWeight,ProductDepth, ProductWidth, ProductHeight))

NewProd  <- dplyr::select(NewProd,-c(ProductNum,BestSellersRank,ShippingWeight,ProductDepth, ProductWidth, ProductHeight))
#BAD EXAMPLE: ExistProd <- ExistProd[,-c(2,12:16)]
            #NewProd    <- NewProd[,-c(2,12:16)]
```
## 1.3.Checking for outliers
```{r warning=FALSE}
#We find lots of outliers in almost all columns. If we remove them, it will drastically change our dataset (already very small), and so we don't remove all of them.
ggplot(stack(ExistProd), aes(x=ind, y=values)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 45, hjust = 1))

#But we should look more in depth at least in the outliers of the dependent column
ggplot(ExistProd, aes(x=ProductType, y=Volume)) +geom_boxplot() + theme(axis.text.x = element_text(angle = 45, hjust = 1))

#We have few outliers here as well. The R Built-in function will tell us the values.
boxplot(ExistProd$Volume, plot = FALSE)$out
#But we only want to remove the two extreme outliers because our dataset is small, and because these outliers don't belong to the product types we want to predict.
ExistProd <- ExistProd[-which(ExistProd$Volume > 7000),]
```
## 1.4.Scaling values
```{r}
#Since different variables have different units, we are going to scale all numeric variables (except label):
for (i in c(2:11)){ExistProd[,i] <- scale(ExistProd[,i])}

#We do the same in NewProd df
for (i in c(2:11)){NewProd[,i] <- scale(NewProd[,i])}
```
<a name="Feature Engineering"></a>  
  
## 2. FEATURE ENGINEERING
## 2.1.Dealing with non-numeric features (Dummifying)
```{r}
#We are going to dummify(turn categorical values into logical ones)
#We need to dummify Product Type only. We check if it's a factor first
str(ExistProd$ProductType)

#The Correlation Matrix is only going to work with numeric values, so we create another df as to avoid messing with the current one, so that we can run a correlation matrix. We do this before dummifying, because once we dummify we'll have lots of variables and the correlation matrix will be way harder to read.
ExistProd_corr <- ExistProd[,-c(1)]

CorrData2 <- cor(ExistProd_corr)
corrplot(CorrData2, order="hclust", method = "number",
        tl.col = "black", tl.srt = 90 , tl.cex = 0.7, tl.pos = "t")

#In order to find out the relationship between the label and the ProductType (categorical), we are going to use the ANOVA test.
ANOVA <- aov(ExistProd$Volume~ ExistProd$ProductType)
summary(ANOVA)
#Since the p-value is higher than 0.05, we reject the Null Hypothesis, which states that both variables come from the same population. Therefore, it's not useful to use this variable to predict Volume.

#Now we will confirm this with a Random Forest w/ dummyfeatures
ExistProd2 <- createDummyFeatures(obj = ExistProd, cols = "ProductType")
NewProd2   <- createDummyFeatures(obj = NewProd, cols = "ProductType")

set.seed(107)

inTrain  <- createDataPartition(ExistProd2$Volume,p = 0.75, list = FALSE)
training <- ExistProd2[inTrain,]
testing  <- ExistProd2[-inTrain,]
ctrl     <- trainControl(method = "cv", number = 10)


mRF  <- randomForest(Volume ~., ExistProd2, ntree = 80)
plot (mRF, main = "Performance of RF depending on the number of trees")
ctrl <- trainControl(method="repeatedcv",repeats = 3, number = 5) #,classProbs=TRUE,summaryFunction = twoClassSummary)
mRF2 <- caret::train(Volume ~ ., data = training, method = "rf", trControl = ctrl, preProcess = c("center","scale"), tuneLength = 2)

varImpPlot(mRF, main = "Performance of RF depending on the number of trees")

#As a conclusion, we get rid of Product Type
ExistProd$ProductType <- NULL


#ExistProd2 <- createDummyFeatures(obj = ExistProd, cols = "ProductType")
#NewProd2   <- createDummyFeatures(obj = NewProd, cols = "ProductType")
```
## 2.2.Dealing with Collinearity
```{r}
#We now look for collinearity in the newly dummified df
CorrData <- cor(ExistProd)
CorNames <- findCorrelation(CorrData, cutoff = 0.9, verbose = TRUE, names = TRUE)
#The above function recommends what columns we should erase based on collinearity. So we proceed to do that:
ExistProd <- ExistProd[, - which(names(ExistProd) %in% CorNames)]

#BAD PRACTICE
#ExistProd[ ,c(2,4,5)] <- list(NULL)
#NewProd[ ,c(2,4,5)]   <- list(NULL)
```
<a name="Modelling"></a>  
  
## 3. Modelling 
```{r warning=FALSE}
set.seed(107)

inTrain  <- createDataPartition(ExistProd2$Volume,p = 0.75, list = FALSE)
training <- ExistProd2[inTrain,]
testing  <- ExistProd2[-inTrain,]
ctrl     <- trainControl(method = "cv", number = 10)

nrow(training)
nrow(testing)

#The chosen models are looped below
Five_Models   <- c("lm", "rf", "knn", "svmLinear", "gbm")

#We create an empty variable so we can later assign all results to it
compare.model <- c()

#We run all models at once and assign the results in 'compare.model'.
#However, now the loop is overwriting each model as it goes through them, so it will only keep the last one saved.
for (i in Five_Models){
  model         <- caret::train(Volume ~., data = training, method = i, )
  pred          <- predict(model, newdata = testing)
  pred.metric   <- postResample(testing$Volume, obs = pred)
  compare.model <- cbind(pred.metric, compare.model)
}

#That's why we create a list with all models so that we can later choose the model
methods <- list()

#We will save them in the variable previously created
for (i in Five_Models) {
  methods[[i]] <- caret::train(Volume ~., data = training, method = i )
}
  
methods

colnames(compare.model) <- Five_Models
compare.model
```
<a name="Analyzing and Plotting Errors"></a>  
  
## 4.Analyzing and plotting errors
```{r}
compare.model.melt <- melt(compare.model, varnames = c("metric", "model"))
compare.model.melt <- as.data.frame(compare.model.melt)
compare.model.melt

#All models offer quite different results, which indicates the predictions will have high variance between models.  
#Based on errors, the SVM stands out in MAE (smaller error than others). RMSE is pretty similar in all. As for the RSquared, RF performes better than SVM here, but SVM comes in second, so we choose this model.
for(i in c("RMSE","Rsquared","MAE")) {
  metric <-  compare.model.melt %>%  filter(metric == i)
  gg     <- ggplot(metric, aes(model,value))
  print(gg + geom_bar(stat = "identity") + ggtitle(i))
}
```
<a name="Final Predictions"></a>  
  
## 5.Final Predictions
```{r}
predictions_svm <- predict(methods$svmLinear, NewProd2)
predictions_svm

#Adding our predictions to the test set
Prod_Sales_Pred                 <- NewProd_Raw[,-c(3:nrow(NewProd_Raw))]
Prod_Sales_Pred$predictions_svm <- predictions_svm
Prod_Sales_Pred                 <- Prod_Sales_Pred[-c(10:11,16:24),]


Prod_Sales_Pred$ProductNum <- mgsub(x = Prod_Sales_Pred$ProductNum,pattern = c(171,172,173,175,176,178,180,181,183,193,194,195,196), replacement = c("Dell1","Dell2","Apple","Toshiba","Razer","hp","Acer","Asus","Samsung1","Motorola1","Samsung2","HTC","Motorola2"))

#We can observe how sales vary among the different products
ggplot(Prod_Sales_Pred, aes(x=ProductNum,y=predictions_svm, fill=ProductType)) + geom_col() + theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}

```